Wissenschaftliches Arbeiten

### 2014-06-29 paper.tex
Rephrased and extended the explanation of different fair division strategies

There is also the criteria of envy-freeness where everyone should receive a selection so that he or she does not want to switch it with the selection of one the others. Another fairness criteria could be that the minimum utility is maximized. This also leads to a more equal allocation which for instance is an important allocation strategy for political decisions and better suited than maximizing the overall utility.~\cite[Chapter~5]{BCE12}

>>>>

There is also the criteria of envy-freeness where everyone should receive a selection so that he or she does not want to switch it with the selection of one the others. Another fairness criteria could be that the utility of the least happy agent is maximized and therefore nobody is left behind, even if this means that the overall satisfaction shrinks. So this strategy leads to a more equal allocation which for instance is important for political decision making where it suits better than maximizing the overall utility.~\cite[Chapter~5]{BCE12}
